\SW Extended! Snappy Titles!

### 2015-05-25 doc/sw-extended.tex
online rule added

\begin{align}
  PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[C_{ij} =
  z_{j}]}{NL_{i}^{k} + M + 1} \\
  PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[C_{ij} =
  z_{j}]}{ND_{i}^{k} + M + 1}
\end{align}
where $ND_{i}^{k}$ and $NL_{i}^{k}$ refer to the number of training lenses and
training duds observed by the $i$-th volunteer at time $k$, $z_{j}$ refers
to the true state of the $j$-th image, and $M = 4$ is a smoothing factor
empirically derived to smooth the skill classification of new volunteers.

@@

In practice we have training images where $p_{j}$ is known. In those
cases we can use the true value when doing the M-Step.

@@

@@

>>>>

\begin{align}
  PL_{i}^{(k + 1)} &= \frac{PL_{i}^{k} (NL_{i}^{k} + M) + \mathbb{I}[C_{ij} =
  z_{j}]}{NL_{i}^{k} + M + z_{j}} \\
  PD_{i}^{(k + 1)} &= \frac{PD_{i}^{k} (ND_{i}^{k} + M) + \mathbb{I}[C_{ij} =
  z_{j}]}{ND_{i}^{k} + M + z_{j}}
\end{align}
where $ND_{i}^{k}$ and $NL_{i}^{k}$ refer to the number of training lenses and
training duds observed by the $i$-th volunteer at time $k$, $z_{j}$ refers to
the true state of the $j$-th image (1 is LENS, 0 is DUD), and $M = 4$ is a
smoothing factor empirically derived to smooth the skill classification of new
volunteers.

@@

In practice we have training images where $p_{j}$ is known. In those
cases we can use the true value when doing the M-Step. We can also choose to
perform the M-step using only the training images (a supervised learning
approach), giving us another handle on quantifying the impact and importance of
simulated training images.

@@

An easy way to conceptualize the previous section is to note that the
Expectation Maximization takes advantage of the fact that each classification
is supposed to be independent of the others and so can be treated as though all
classifications were made at the same time.  The repetition of the steps
ensures that the parameters are self-consistent.

@@

\subsubsection{Online}

Like in the binomial case, the multinomial case can be performed online, where
each new piece of information updates an existing assessment of lens
classification and user skill. If a new classification $C_{iju}^{(k + 1)}$ is
made, then by Bayes' Theorem the updates are as follows (with $i$, $j$, $u$,
and $v$ acting as fixed indices):
\begin{align}
  p_{jv}^{(k + 1)} &= \left( \frac{P^{k}_{ivu}^{C_{iju}^{(k + 1)}}}{\sum_{v'}
  p_{jv'}^{k} P^{k}_{iv'u}^{C_{iju}^{(k+1)}}} \right) p_{jv}^{k} \\
  P^{(k+1)}_{ivu}  &= \frac{C^{(k+1)}_{iju} p^{k}_{jv} + P^{k}_{ivu} \sum_{j'\in
  \Omega_i} p^{k}_{j'v} }{p^{k}_{jv} + \sum_{j'
  \in \Omega_i} p^{k}_{j'v}}
\end{align}
If we are using only a supervised learning set, then $p^k_{j'v} \in (0, 1)$.
